High Mass Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors

### 2012-03-30 paper.tex
Changes before sending to Ib and Ole

\begin{abstract}
We demonstrate a combined microreactor and time of flight system for testing and characterization of heterogeneous catalysts with high resolution mass spectrometry and high sensitivity. Catalyst testing is performed in silicon-based microreactors which have high sensitivity and fast thermal response. Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source. The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to $\Delta$m/m$>$2500. The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatopgraphy not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration). As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
\end{abstract}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems. As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}. Such a platform have been developed previously to test and characterize model catalysts in our department\cite{Henriksen2009}. However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance. Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements. The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome. The QMS is additionally subject to a low mass range (typically $\sim$100-200\,amu) limiting general use. Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution. This is at the expense of acquisition of full mass spectra during the experiment limiting operation by potentially losing interesting features in other masses not monitored. Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures. As an alternative to gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz) and mass range only limited by the detector. For standard available microchannel plate (MCP) as detector a mass range of 0--5000\,amu can be obtained.

Typically TOF-MS in heterogeneous catalysis is used as a surface analytic tool, i.e. TOF-SIMS\cite{Benninghoven1994,DeSmet1998,Grams2004,Johnson2010}. Measurements of reactants and products on heterogeneous catalysts by TOF-MS have previously been performed\cite{Levy1963,Okumura2007} but, until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated. Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing of heterogeneous catalysts.

@@

The catalyst under investigation is deposited in the microreactor reactor volume by e.g. evaporation\cite{Henriksen2009}, drop casting\cite{Vesborg2010} or gas aggregation formed size-selected nanoparticles. The gas composition in the microreactor reactor volume is ionized by the ion gauge and is subsequently detected by the TOF-MS which is connected to the microreactor capillary outlet. A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}.
\begin{figure}
 \includegraphics[width=14cm]{TOF_microreactor.png}%
 \caption{Schematic of the total system (not to scale)\label{fig:TOF_microreactor}}%
\end{figure}
The setup consists of three main components. The microreactor, where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF-MS used for gas analysis. A QMS is furthermore connected to the capillary of the microreactor which enables direct comparison between the QMS and TOF-MS.

\subsection{The microreactor platform}
Catalyst characterization and performance evaluation is performed in a microreactor platform \cite{Henriksen2009}. The microreactors are silicon-based and measures 20x15\,mm. The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used to restrict the gas flow from the reactor volume. The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL volume. The two gas inlets are combined on the chip where the inlet gases mix by diffusion. The capillary is designed such that approximately $3\times10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar. Any surplus of gas from the two inlets that does not enter the reactor volume is directed through an outlet to a turbo pump. The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, is detected by mass spectrometry ensuring high sensitivity.

@@

\subsubsection{Data treatment}
Raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}. Here the closely lying peaks from OH$^{+}$ from cracking of both residue water and water as reaction product and uncombusted NH$_3^{+}$ is shown. The ability to separate these contributions substantially simplifies quantification of ammonia and allows for easier characterization of catalyst performance. 
\begin{figure}
 \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
 \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS. The entire graph section represents a mass difference of 100\,milli-amu.\label{fig:gaussian_fit}}%
\end{figure}
In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS. At constant MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is $\sim$400. 
\begin{figure}
 \includegraphics[width=14cm]{dynamic_range.png}%
 \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum (integrated area indicated in each panel). As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits. The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
\end{figure}
In reality the dynamic range is limited mostly by the data acquisition hardware as well as the quality of the ion source. Even with our very simple home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim$1000 using an integration time of $\sim$5\,s. The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range while covering a much larger mass range.

Since the TOF-MS only measures flight time and not the actual mass of the measured molecules or atoms it is necessary to determine the relationship between flight time and actual mass. This can be done by calibration masses expressing known patterns in the mass spectrum. In this way masses can be reasonably determined with subsequent fitting of these values to get an expression for the flight time as a function of mass. This approach is in some cases adequate but does have the significant drawback that several peaks of well known mass must be present in the flight spectrum which is not always necessarily the case. To determine the relationship between mass and flight time we have made a numeric model of the mass spectrometer which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$ and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass. Typically, the model is used together with the experimental determination of a single mass since this will help fix the unknown delays originating from the measurement trigger, rise time of the high-voltage pulse at the repeller plate and cable delays. As seen in Figure~\ref{fig:model_error} the performance of the model is surprisingly good despite its simplicity. The model is written in Python and can be acquired online\cite{ModelGithub}.
\begin{figure}
 \includegraphics[width=14cm]{model_error.png}%
 \caption{Comparison of the simulated model (red line, top panel) to actual measured experimental values (blue dots). In the bottom panel the difference between acquired experimental data and data calculated from the model is plotted, errorbars represents only the uncertainty in the experimental data. As seen from the figure a deviation of $\sim$100\,ns at 70\,amu is present.\label{fig:model_error}}%
\end{figure}

\section{Oxidation of ammonia}
To demonstrate the system capability ammonia oxidation on platinum thin films has been used as test reaction. The catalytic oxidation of ammonia can proceed along primarily three different routes.
\begin{equation}
4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
\label{eq:Pt_clean_combustion}
\end{equation}
\begin{equation}
2NH_3+2O_2\rightarrow N_2O + 3H_2O
\end{equation}
\begin{equation}
4NH_3+5O_2\rightarrow 4NO + 6H_2O
\end{equation}
All of these systems are difficult to analyze both qualitatively and quantitatively due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion and is a part of the residue gas. Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17. Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis. Often a charge to mass ratio without cracking from either products or residue gas in the system is used to quantify the amount of ammonia and water. In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen since water does not contribute to these masses. However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are both processes with very low yields. The measurement of these masses have a very poor signal to noise ratio making measurements on ammonia very difficult with traditional mass spectrometry methods.

At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 4:3 ratio corresponding to stoichiometry for this reaction. After equilibration the temperature is increased in steps from room temperature to 190\,$^{\circ}$C. The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.
\begin{figure}
 \includegraphics[width=14cm]{ammonia_reactivity.png}%
 \caption{Ammonia oxidation as a function of temperature on a 10\% geometrical coverage Pt thin film. As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$. Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses.\label{fig:ammonia_reactivity}}%
\end{figure}
In Figure~\ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown. At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu. As seen from Figure~\ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C. The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature\cite{Imbihl2007,Zeng2009}.

@@

\section{Summary}
We have demonstrated a combined microreactor and TOF-MS system which can be employed to test and characterize model heterogeneous catalysts. An automated gas handling system is used to flow gas over a catalyst in the microreactor volume from where gases can be probed. The reactor gas composition is directed through a flow restriction in the microreactor and subsequently analyzed by a TOF-MS combining high sensitivity and high mass resolution.

As a demonstration of the system ammonia oxidation on platinum thin films was performed. The ability to resolve OH$^{+}$ and NH$_3^+$ which is separated by 23\,milli-amu was demonstrated. The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal. This greatly simplifies the analysis compared to conventional QMSs used for gas analysis. The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu.

\section{Acknowledgements}

>>>>

\begin{abstract}
We demonstrate a combined microreactor and time of flight system for testing and characterization of heterogeneous catalysts with high resolution mass spectrometry and high sensitivity. Catalyst testing is performed in silicon-based microreactors which have high sensitivity and fast thermal response. Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source. The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to $\Delta$m/m$>$2500. The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatopgraphy not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration). As a demonstration of the system we here present data from ammonia oxidation on 5\,nm Pt nanoparticles showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
\end{abstract}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems. As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}. Such a platform has been developed to test and characterize model catalysts in our department\cite{Henriksen2009}. However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance. Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements. The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome. The QMS is additionally subject to a low mass range (typically $\sim$100-200\,amu) limiting general use. Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution. This is at the expense of acquisition of full mass spectra during the experiment limiting operation by potentially losing interesting features in other masses not monitored. Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures. As an alternative to gas chromatography or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz) and mass range only limited by the detector. For standard available microchannel plate (MCP) as detector a mass range of 0--5000\,amu can be obtained.

Typically TOF-MS in heterogeneous catalysis is used as a surface analytic tool, i.e. TOF-SIMS\cite{Benninghoven1994,DeSmet1998,Grams2004,Johnson2010}. Measurements of reactants and products on heterogeneous catalysts by TOF-MS have previously been performed\cite{Levy1963,Okumura2007} but, until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS has not been demonstrated. Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing of heterogeneous catalysts.

@@

The catalyst under investigation is deposited in the microreactor reactor volume by e.g. evaporation\cite{Henriksen2009}, drop casting\cite{Vesborg2010} or gas aggregation formed size-selected nanoparticles. The gas composition in the microreactor reactor volume is ionized by the ion gauge and is subsequently detected by the TOF-MS which is connected to a capillary outlet on the microreactor. A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}.
\begin{figure}
 \includegraphics[width=14cm]{TOF_microreactor.png}%
 \caption{Schematic of the total system (not to scale)\label{fig:TOF_microreactor}}%
\end{figure}
The setup consists of three main components. The microreactor, where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF-MS used for gas analysis. A QMS is furthermore connected to the capillary of the microreactor which enables direct comparison between the QMS and TOF-MS.

\subsection{The microreactor platform}
Catalyst characterization and performance evaluation is performed in a microreactor platform \cite{Henriksen2009}. The microreactors are silicon-based and measures 20x15\,mm. The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used to restrict the gas flow from the reactor volume. The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL. The two gas inlets are combined on the chip where the inlet gases mix by diffusion. The capillary is designed such that approximately $3\times10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar. Any surplus of gas from the two inlets that does not enter the reactor volume is directed through an outlet to a turbo pump. The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, is detected by mass spectrometry ensuring high sensitivity.

@@

\subsubsection{Data treatment}
Raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}. Here the closely lying peaks from OH$^{+}$ from cracking of both residue water and water as reaction product and uncombusted NH$_3^{+}$ is shown. The ability to separate these contributions substantially simplifies quantification of ammonia and allows for easier characterization of catalyst performance. 
\begin{figure}
 \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
 \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS. The entire graph section represents a mass difference of 100\,milli-amu.\label{fig:gaussian_fit}}%
\end{figure}
In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS. At constant MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is $\sim$400. 
\begin{figure}
 \includegraphics[width=14cm]{dynamic_range.png}%
 \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum (integrated area indicated in each panel). As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits. The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
\end{figure}
In reality the dynamic range is limited mostly by the data acquisition hardware as well as the quality of the ion source. Even with the home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim$1000 using an integration time of $\sim$5\,s. The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range while covering a much larger mass range.

Since the TOF-MS only measures flight time and not the actual mass of the measured molecules or atoms it is necessary to determine the relationship between flight time and actual mass. This can be done by calibration masses expressing known patterns in the mass spectrum. In this way masses can be reasonably determined with subsequent fitting of these values to get an expression for the flight time as a function of mass. This approach is in some cases adequate but does have the significant drawback that several peaks of well known masses must be present in the flight spectrum which is not always necessarily the case. To determine the relationship between mass and flight time we have made a numeric model of the mass spectrometer which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$, and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass. Typically, the model is used together with the experimental determination of a single mass since this will help fix the unknown delays originating from the measurement trigger, rise time of the high-voltage pulse at the repeller plate and cable delays. As seen in Figure~\ref{fig:model_error} the performance of the model is good despite its simplicity giving a total error in flight time estimation of $\sim$100\,ns at 70\,amu. The model is written in Python and can be acquired online\cite{ModelGithub}.
\begin{figure}
 \includegraphics[width=14cm]{model_error.png}%
 \caption{Comparison of the simulated model (red line, top panel) to actual measured experimental values (blue dots). In the bottom panel the difference between acquired experimental data and data calculated from the model is plotted, errorbars represents only the uncertainty in the experimental data. As seen from the figure a deviation of $\sim$100\,ns at 70\,amu is present.\label{fig:model_error}}%
\end{figure}

\section{Oxidation of ammonia}
To demonstrate the system capability ammonia oxidation on a 40\,\% geometrical coverage 5\,nm Pt nanoparticles has been used as test reaction. The catalytic oxidation of ammonia can proceed along primarily three different routes.
\begin{equation}
4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
\label{eq:Pt_clean_combustion}
\end{equation}
\begin{equation}
2NH_3+2O_2\rightarrow N_2O + 3H_2O
\end{equation}
\begin{equation}
4NH_3+5O_2\rightarrow 4NO + 6H_2O
\end{equation}
All of these systems are difficult to analyze both qualitatively and quantitatively due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion and is a part of the residue gas. Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17. Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis. Often a charge to mass ratio without cracking from either products or residue gas in the system is used to quantify the amount of ammonia and water. In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen since water does not contribute to these masses. However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are both processes with very low yields. The measurement of these masses have a very poor signal to noise ratio making measurements on ammonia very difficult with traditional mass spectrometry methods.

At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 4:3 ratio corresponding to stoichiometry for this reaction. After equilibration the temperature is increased in steps of ?? from room temperature to 190\,$^{\circ}$C. The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.
\begin{figure}
 \includegraphics[width=14cm]{ammonia_reactivity.png}%
 \caption{Ammonia oxidation as a function of temperature on a 40\,\% geometrical coverage 5\,nm Pt nanoparticles. As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$. Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses.\label{fig:ammonia_reactivity}}%
\end{figure}
In Figure~\ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown. At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to 70 amu. As seen from Figure~\ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C. The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature\cite{Imbihl2007,Zeng2009}.

@@

\section{Summary}
We have demonstrated a combined microreactor and TOF-MS system which can be employed to test and characterize model heterogeneous catalysts. An automated gas handling system is used to flow gas over a catalyst in a microreactor volume from where gases can be probed. The reactor gas composition is directed through a flow restriction in the microreactor and subsequently analyzed by a TOF-MS combining high sensitivity and high mass resolution.

As a demonstration of the system ammonia oxidation on 5\,nm Pt nanoparticles was performed. The ability to resolve OH$^{+}$ and NH$_3^+$ which is separated by 23\,milli-amu was demonstrated. The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal. This greatly simplifies the analysis compared to conventional QMSs used for gas analysis. The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu and can be applied to the study of small amounts of catalysts.

%\section{Acknowledgements}
